% Section: Future Work
\section{Future Work}
\label{sec:future-work}

% TODO: Expand this section.
%
% Potential directions:
% - Formal verification of governance contracts
% - Machine-readable contract specification languages
% - Empirical evaluation of Reflector in production systems
% - Multi-agent coordination under shared governance contracts
% - Adaptive milestone criteria based on historical drift data
% - Integration with CI/CD and DevSecOps pipelines
% - Tooling and IDE integration for contract authoring

Several promising directions for future work emerge from the Reflector framework:

\paragraph{Formal Contract Verification.}
Future work should investigate the application of formal methods—such as temporal logic
and model checking—to provide machine-verified guarantees about governance contract
compliance. This would strengthen the enforcement properties of Reflector beyond the
runtime monitoring approach described in this paper.

\paragraph{Empirical Evaluation.}
The theoretical framework presented here requires empirical validation through controlled
studies and case analyses of Reflector deployments in production AI-augmented development
environments. Metrics of interest include drift detection latency, false positive rates
in invariant monitoring, and the effect of milestone granularity on development velocity.

\paragraph{Adaptive Milestone Criteria.}
Static milestone criteria may be suboptimal across diverse project types and team
contexts. Future work should explore adaptive milestone specification that adjusts
validation criteria based on historical drift patterns and project-specific risk profiles.

\paragraph{Multi-Agent Governance.}
The current framework addresses single-agent and hierarchical agent topologies.
Future work should extend Reflector's governance model to peer-to-peer multi-agent
systems where no single agent has supervisory authority.
